---
title: Financial applications of blockchains and distributed ledgers
short-title: Blockchain Technologies
author: "Jiahua (Java) Xu"
date: "Session 4"
output:
  beamer_presentation:
    colortheme: beaver
    fonttheme: structurebold
    highlight: haddock
    includes:
      in_header: diss-beamer.sty
    slide_level: 2
    theme: Dresden
    keep_tex: yes
  slidy_presentation:
    footer: "Blockchain applications, Jiahua (Java) Xu, EPFL"
  ioslides_presentation:
    logo: figure/epfllogo.png
subtitle: Master's program in Financial Engineering
link-citations: yes
bibliography: BlockchainEconomics.bib
# suppress-bibliography: no
...

```{r echo=F, warning=F}
library(magrittr)
options(stringsAsFactors=F)

knitr::opts_chunk$set(echo = F, cache = T, eval=F)
```

```{r child = 'session4.Rmd', eval=T}
```

## Thank you!

**Contact**

\vspace{0.6cm}

Jiahua (Java) Xu

\vspace{0.4cm}

Ecole Polytechnique Fédérale de Lausanne (EPFL)


EXTRA 249 (Extranef UNIL)


Quartier UNIL-Dorigny 


\vspace{0.4cm}

jiahua.xu@epfl.ch

## References {.allowframebreaks}

\widowpenalties 1 0