---
title: Blockchain Technologies
author: "Jiahua (Java) Xu"
date: "Term 2, 2021"
output:
  beamer_presentation:
    colortheme: crane
    fonttheme: structurebold
    highlight: haddock
    pandoc_args: ["--syntax-definition=solidity.xml"]
    includes:
      in_header: diss-beamer.sty
    slide_level: 2
    theme: Dresden
    keep_tex: yes
  ioslides_presentation:
    logo: figure/ucllogo.svg
  slidy_presentation:
    footer: "Blockchain Technologies"
subtitle: UCL Computer Science
link-citations: yes
bibliography: Blockchain.bib
# suppress-bibliography: no
...

```{r echo=F, warning=F}
library(magrittr)
options(stringsAsFactors=F)

knitr::opts_chunk$set(echo = F, cache = T, eval=F)
```

```{r child = 'sessions/housekeeping_UCL_2022.Rmd', eval=T}
```

```{r child = 'sessions/resources.Rmd', eval=T}
```

## Thank you!

**Contact**

\vspace{0.6cm}

Jiahua (Java) Xu

\vspace{0.4cm}

UCL Centre for Blockchain Technologies


66-72 Gower Street



\vspace{0.4cm}

jiahua.xu@ucl.ac.uk

## References {.allowframebreaks}

\widowpenalties 1 0